---
title: "Dplyr Data Manipulation"
author: "Long Nguyen"
date: "1/14/2019"
output: html_document
---

## Chapter 1: Introduction to Dplyr and tbls
In this introduction and exercises, the dataset **hflights** will be used.

```{r}
library(dplyr)  #loading necessary package
library(hflights)
head (hflights)
```

```{r}
#Convert the hflights into a tibble
hflights_tibble <- as_tibble(hflights)
head (hflights_tibble)
carriers <-  hflights_tibble$UniqueCarrier
head (carriers)
```
In this exercise, I was introduce to another way to convert abbreviation in the tbl into full name. For example, abbr of carriers were converted into its full name such as *AA* for *American Airline*, etc.

```{r}
  lut <- c("AA" = "American", "AS" = "Alaska", "B6" = "JetBlue", "CO" = "Continental", "DL" = "Delta", "OO" = "SkyWest", "UA" = "United", "US" = "US_Airways", "WN" = "Southwest", "EV" = "Atlantic_Southeast", "F9" = "Frontier", 
  "FL" = "AirTran", "MQ" = "American_Eagle", "XE" = "ExpressJet", "YV" = "Mesa")
  carriers <- lut[carriers]
  hflights$Carrier <- carriers
  glimpse(hflights)
```

The *original* hflights contains a **Cancellation Code** with values "A, B, C, D, and '' ". The codes below will convert these codes into something readable.

```{r}
  hflights$CancellationCode[hflights$CancellationCode ==""] <- "E" # Need to convert "" to "E"
  lut <- c("A" = "carrier", "B" = "weather", "C" = "FFA", "D" = "security", "E" = "not cancelled")
  hflights$Code <- lut[hflights$CancellationCode]
  glimpse(hflights)
```

