---
title: "MyNotes"
author: "LongNguyen"
date: "1/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the Gapminder and dplyr packages.
Need to load both gapminder and dplyr for this course.
Using filter with pipe %>%.
For example, using gapminder %>% filter (year ==2007) will filter dataframe for year =2007

```{r}
library (gapminder)
library (dplyr)
gapminder %>% filter (country == "United States")
```

## Arranging observations by life expectancy
```{r}
gapminder %>% arrange(lifeExp)  #Arrange by life expectancy ascending order
gapminder %>% arrange(desc(lifeExp))
```

## Using a combination of filter and arrange

```{r}
# Filter for the year 1957, then arrange in descending order of population
gapminder %>% filter(year == 1957) %>% arrange(desc(pop))
```

## Mutate
mutate () function can be used to either change the exisiting column value, or adding new column to the dataframe.PLEASE remember that calling pipe on mutate only affect the return dataframe, not the original gapminder dataframe.

## Data visualization with ggplot2
Example of displaying population and gdpPercap for year 1952
```{r}
library(ggplot2)  # Need to load the library first.
ggplot(gapminder %>%filter(year==1952), aes(x=pop, y= gdpPercap)) + geom_point()
```

Introducing log_scale by adding: scale_x_log10() or scale_y_log10()
```{r}
gapminder_2002 <- gapminder %>% filter(year == 2002)
ggplot(gapminder_2002, aes (x= pop, y= lifeExp, color = continent, size = gdpPercap)) + geom_point()+ scale_x_log10()
```

Dividing graph by using faceting
```{r}
ggplot(gapminder, aes(x= gdpPercap, y= lifeExp, color = continent, size=pop)) + geom_point() + scale_x_log10() + facet_wrap(~year)

```

