---
title: "Introduction To Data"
author: "LongNguyen"
date: "1/14/2019"
output: html_document
---

## Chapter 1
This chapter will use the dataset from *openintro* and *dplyr* package.
some of the new functions that I learned in this chapter are:
1.  glimpse() which is part of the *dplyr* package. This function is similar to the str() function.
2.  droplevels () **Use with factor data where some levels are unused**
3.  mutate(read_cat = ifelse(read < avg_read, "below average", "at or above average"))  Create and assign values to new category of dataframe.$
4.  case_when()   See help() page of this function. Similar to switch_case in other language.

```{r echo=FALSE}
library(openintro)
library(dplyr)
str(email50)  # Review struction of email50

```
Example of case_when()
```{r echo= FALSE}
# Create number_yn column in email50
email50_fortified <- email50 %>%
  mutate(
    number_yn = case_when(
      # if number is "none", make number_yn "no"
      number =="none" ~ "no", 
      # if number is not "none", make number_yn "yes"
      number != "none" ~ "yes"  
    )
  )
  

# Visualize the distribution of number_yn
ggplot(email50_fortified, aes(x = number_yn)) +
  geom_bar()
```

## Chapter 2
