---
title: "Intermediate_R_Practice"
author: "LongNguyen"
date: "1/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Conditionals and Control Flow
**Description:** Suppose you're a student in a prestigious academy that only allows the country's best 200 students every year. Just for fun, you decide to analyze the grades of this academy. The highest possible grade is 100, the lowest possible grade is 0.

You have access to your own grades, to anonymized grades for all of your 199 classmates, and for the 200 pupils in the previous 4 years. This data is available in your workspace as `me`, `other_199`, and `previous_4`, respectively. Have a look at these variables in the console.

To format our data so that it'd be easier to work with and analyze later on, let's merge the three datasets to one called `last_5`, with dimensions 200 by 5. That is, last_5 contains all 200 scores from the last 5 classes.

`me`, `other_199`, and `previous_4` are available in your workspace.

Grades of `me`, `other_199`, and `previous_4` are entered by generating a random number using sample function
```{r}
me <- 89 # This is the grade assigned - not random number
other_199 <- sample(c(50:100), 199, replace= TRUE) # Assigned random number to this variable. Replace=TRUE
previous_4 <- matrix(sample(c(50:100), 800, replace= TRUE), nrow = 200, ncol = 4)
paste("Other_199 grades: ", head(other_199)) # Showing sample of other_199 grades
```

#### First Exercise:

```{r}
my_class <- c(me, other_199) # Combined my grade with others in my class
last_5 <- cbind(my_class, previous_4)  # combined my_class with previous_4 matrix to create last 5 years grades
nms <- paste0("year_",1:5)
colnames(last_5) <-  nms
head (last_5)
```

#### Second & Third Exercise: 
Skip this

#### Fourth Exercise:
Use `sum()` to count the number of values in vector that meet the condition based on TRUE = 1, FALSE=0
Use `mean()` to count the proportion of grades
```{r}
sum(my_class>75)
sum(my_class>me)
mean(last_5<=64)
```
